---
title: "MCF10A metabolism screen"
author: "Marion Hardy"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true 
    theme: spacelab 
    highlight: monochrome
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, cache = TRUE, echo = FALSE, warning = F, cache.lazy = F)
knitr::opts_chunk$set(fig.width=10, fig.height=15) 

library(RColorBrewer)
library(tidyverse)
library(DESeq2)
library(tidyverse)
library(cowplot)
library(biomaRt)
library(ggrepel)
library(RColorBrewer)
library(pheatmap)
library(xlsx)
library(msigdbr)
library(clusterProfiler)
library(NMF)
library(org.Hs.eg.db)
library(ReactomePA)
```

```{r Data loading, include=FALSE}

counts <- as.data.frame(read.csv("./data/MCF10A_counts.csv", row.names = 1))
coldata = read.csv("./data/coldata.csv")
counts = counts[,-1]

```

# Introduction

Analysis of MCF10A in 16 different conditions 2 biological replicates
per sample

This report was made following John's suggestion to check the difference between the samples separated by PC1.

# Create new coldata

Add to the metadata to group the PC1 left group (EGF Oligo and growth medium) vs all other samples.

```{r, fig.height=4, fig.width=6}

coldata$PC1 = c("out","out", rep("others",4),
                "OlEGF","OlEGF", rep("others",16),
                "OlEGF","OlEGF", rep("others",6))

write.csv(coldata,"./data/coldata.csv")

dds <- DESeqDataSetFromMatrix(countData = counts, colData = coldata,
                              design = ~PC1+replicate) 

dds$PC1 <- relevel(dds$PC1, "others")
dds <- DESeq(dds)

#saveRDS(dds, file = "./data_output/PC1_OlEGF_vs_others_dds.rds")

```

# PCA

## All conditions

```{r, fig.height=6, fig.width=12}
# Checking PCA

rld <- vst(dds)
assay(rld) <- limma::removeBatchEffect(assay(rld), rld$replicate)

p1 <- plotPCA(rld,intgroup="PC1") + 
  geom_text_repel(max.overlaps = 15,
                  box.padding = 0.25,
                  segment.color = 'grey50',
                  fontface = "italic",
                  label = rld$PC1)+
  labs(title = 'PCA per PC1')

p2 <- plotPCA(rld,intgroup="condition") + 
  geom_text_repel(max.overlaps = 15,
                  box.padding = 0.25,
                  segment.color = 'grey50',
                  fontface = "italic",
                  label = rld$condition)+
  labs(title = 'PCA per condition')

plot_grid(p1, p2, ncol = 2, align = "hv")

```


```{r}

p2 <- plotPCA(rld,intgroup="condition") + 
  geom_text_repel(max.overlaps = 15,
                  box.padding = 0.25,
                  segment.color = 'grey50',
                  fontface = "italic",
                  label = rld$condition)+
  theme_bw()+
  labs(title = 'PCA per condition')

print(p2)

ggsave(plot = p2, "./figures/PCA.svg", device = "svg", dpi = 300,
       height = 5, width = 7)

```

# Heatmap of z score

```{r, fig.height=60, fig.width=10}

diff = read.xlsx("./data_output/PC1_OlEGF_vs_others/Sign_genes.xlsx", sheetName = 'SIGNIF')

reslog = vst(dds, blind = FALSE)
mat = assay(reslog)

coldata = as.data.frame(colData(reslog))
colnames(mat) = rownames(coldata)

# Do the scaling to get z-scores

basemean = rowMeans(mat)
mats = t(apply(mat, 1, scale))
colnames(mats) = colnames(mat)

mats = mats[diff$ensembl,]
rownames(mats) = diff$gene

pheatmap(mats, main="z-score heatmap", cluster_cols=F,
         fontsize_row=3, border_color=NA, scale = "none")

```

# Comparing the EGF+Oligo vs all others (excluding GM)

```{r}

resultsNames(dds) %>% 
  knitr::kable()

res <- results(dds, name = "PC1_OlEGF_vs_others")
res_tbl <- as_tibble(res, rownames="ensembl")

# Import annotation file

ensembl_to_geneName <- readRDS("./data/hsapiens_annotations_230510.rds") %>% 
  filter(!duplicated(gene, drop = F))

# Add gene names and entrez id to your results

res_tbl <- res_tbl %>%
  left_join(ensembl_to_geneName) %>%
  arrange(padj) 

# write.csv(res_tbl,"./data_output/PC1_OlEGF_vs_others/res_tbl.csv", row.names = T)

# plotMA(res) # looks good

# Save the signif genes

# overexpr <- res_tbl %>% filter(padj<=0.05 & log2FoldChange>=1) 
# underexpr <- res_tbl %>% filter(padj<=0.05 & log2FoldChange<=-1)
# signif <- full_join(overexpr, underexpr)

# write.xlsx(overexpr, file="./data_output/PC1_OlEGF_vs_others/Sign_genes.xlsx", sheetName="UP")
# write.xlsx(underexpr, file="./data_output/PC1_OlEGF_vs_others/Sign_genes.xlsx", sheetName="DOWN", append=TRUE)
# write.xlsx(signif, file="./data_output/PC1_OlEGF_vs_others/Sign_genes.xlsx", sheetName="SIGNIF", append=TRUE)

```

### Volcano plots

```{r, fig.height=6, fig.width=8}
# Volcano plot

p1 =
res_tbl %>%
  filter(!is.na(padj)) %>%
  ggplot(aes(x = log2FoldChange, y = -log10(padj),
             color = padj < 0.05 & abs(log2FoldChange) > 1, 
             label = ifelse(padj<0.05&log2FoldChange>=1|
                              padj<0.05&log2FoldChange<=-1,as.character(gene),''))) +
  scale_colour_manual(values = c("gray", "firebrick3")) +
  labs(col="Sign diff expressed")+
  geom_point(size = 0.5) +
  geom_hline(yintercept = -log10(0.05)) +
  geom_vline(xintercept = 1) +
  geom_vline(xintercept = -1)+
  geom_text_repel(max.overlaps = 15,
                  box.padding = 0.25,
                  segment.color = 'grey50',
                  fontface = "italic")+
  labs(title = "PC1 EGF and oligo vs all others")+
  theme_bw()

print(p1)

# ggsave("./figures/PC1_OlEGF_vs_others/volcanoplot.png", last_plot(), dpi= 500, width = 12, height = 8)

```

### GSEA analysis (logFc)

```{r}

ordered_genes_fc <- res_tbl$log2FoldChange
names(ordered_genes_fc) <- res_tbl$gene
ordered_genes_fc <- sort(ordered_genes_fc, decreasing = T)

```

```{r}

# MsigDb

hsa_GOBP_sets <- msigdbr(
  species = "Homo sapiens", 
  category = "C5",
  subcategory = "GO:BP")

hsa_GOMF_sets <- msigdbr(
  species = "Homo sapiens", 
  category = "C5",
  subcategory = "GO:MF")

hsa_GOCC_sets <- msigdbr(
  species = "Homo sapiens", 
  category = "C5",
  subcategory = "GO:CC") 

hsa_reactome_sets <- msigdbr(
  species = "Homo sapiens", 
  category = "C2",
  subcategory = "CP:REACTOME") # for reactome collection

hsa_kegg_sets <- msigdbr(
  species = "Homo sapiens", 
  category = "C2",
  subcategory = "CP:KEGG") # for KEGG collection

hsa_wiki_sets <- msigdbr(
  species = "Homo sapiens", 
  category = "C2",
  subcategory = "CP:WIKIPATHWAYS") # for Wikipathways collection

set.seed(054057) # for reproducibility

```

#### GOBP

```{r, fig.height=18, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_GOBP_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 50, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GO:BP Oligo and EGF vs others")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/PC1_OlEGF_vs_others/GOBPgsea.svg", dpi = 300,
       height =15, width = 8, device = "svg")

# write.xlsx(gsea_results, "./data_output/PC1_OlEGF_vs_others/GOBPgsea.xlsx")

```


```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5, layout = 'fr')+
  scale_colour_gradient2(name = "fold change", 
                         low = "blue", 
                         mid = "white", 
                         high = "red")

```

#### GOMF

```{r, fig.height=9, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_GOMF_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GO:MF Oligo and EGF vs others")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

# ggsave(plot = last_plot(), "./figures/PC1_OlEGF_vs_others/GOMFgsea.svg", dpi = 300,
#        height = 10, width = 8, device = "svg")
# 
# write.xlsx(gsea_results, "./data_output/PC1_OlEGF_vs_others/GOMFgsea.xlsx")

```

```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)+
  scale_colour_gradient2(name = "fold change", 
                         low = "blue", 
                         mid = "white", 
                         high = "red")
```

#### Reactome

```{r, fig.height=8, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_reactome_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "Reactome Oligo and EGF vs others")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/PC1_OlEGF_vs_others/Reactomegsea.svg", 
       dpi = 300, height = 10, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/PC1_OlEGF_vs_others/Reactomegsea.xlsx")

```

```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)+
  scale_colour_gradient2(name = "fold change", 
                         low = "blue", 
                         mid = "white", 
                         high = "red")
```


#### KEGG

```{r, fig.height=8, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_kegg_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "KEGG Oligo and EGF vs others")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

# ggsave(plot = last_plot(), "./figures/PC1_OlEGF_vs_others/KEGGgsea.svg", dpi = 300,
#        height = 8, width = 8, device = "svg")
# 
# write.xlsx(gsea_results, "./data_output/PC1_OlEGF_vs_others/KEGGgsea.xlsx")

```


```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)+
  scale_colour_gradient2(name = "fold change", 
                         low = "blue", 
                         mid = "white", 
                         high = "red")
```

#### Wikipathways

```{r, fig.height=8, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_wiki_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "Wikipathways Oligo and EGF vs others")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

# ggsave(plot = last_plot(), "./figures/PC1_OlEGF_vs_others/wikigsea.svg", dpi = 300,
#        height = 10, width = 8, device = "svg")
# 
# write.xlsx(gsea_results, "./data_output/PC1_OlEGF_vs_others/wikigsea.xlsx")

```


```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)+
  scale_colour_gradient2(name = "fold change", 
                         low = "blue", 
                         mid = "white", 
                         high = "red")
```


# What effects comes from EGF and what comes oligo?

```{r}

coldata$PC1_sep = c("out","out", rep("others",4),
                "EGF","EGF", rep("others",16),
                "Oligo","Oligo", rep("others",6))

# write.csv(coldata,"./data/coldata.csv")

dds <- DESeqDataSetFromMatrix(countData = counts, colData = coldata,
                              design = ~PC1_sep+replicate) 

dds$PC1_sep <- relevel(dds$PC1_sep, "others")

dds <- DESeq(dds)

resultsNames(dds)

## Get EGF vs others
res_egf <- results(dds, name = "PC1_sep_EGF_vs_others")
res_egf_tbl <- as_tibble(res_egf, rownames="ensembl")

res_egf_tbl <- res_egf_tbl %>%
  left_join(ensembl_to_geneName) %>%
  arrange(padj) %>% 
  na.omit()

# write.csv(res_egf_tbl,"./data_output/PC1_EGF_vs_others/res_tbl.csv", row.names = T)

# overexpr <- res_egf_tbl %>% filter(padj<=0.05 & log2FoldChange>=1)
# underexpr <- res_egf_tbl %>% filter(padj<=0.05 & log2FoldChange<=-1)
# signif <- full_join(overexpr, underexpr)
# 
# write.xlsx(overexpr, file="./data_output/PC1_EGF_vs_others/Sign_genes.xlsx", sheetName="UP")
# write.xlsx(underexpr, file="./data_output/PC1_EGF_vs_others/Sign_genes.xlsx", sheetName="DOWN", append=TRUE)
# write.xlsx(signif, file="./data_output/PC1_EGF_vs_others/Sign_genes.xlsx", sheetName="SIGNIF", append=TRUE)

## Get Oligo vs others
res_oligo <- results(dds, name = "PC1_sep_Oligo_vs_others")
res_oligo_tbl <- as_tibble(res_oligo, rownames="ensembl")

res_oligo_tbl <- res_oligo_tbl %>%
  left_join(ensembl_to_geneName) %>%
  arrange(padj) %>% 
  na.omit()

# write.csv(res_oligo_tbl,"./data_output/PC1_oligo_vs_others/res_tbl.csv", row.names = T)

# overexpr <- res_oligo_tbl %>% filter(padj<=0.05 & log2FoldChange>=1)
# underexpr <- res_oligo_tbl %>% filter(padj<=0.05 & log2FoldChange<=-1)
# signif <- full_join(overexpr, underexpr)
# 
# write.xlsx(overexpr, file="./data_output/PC1_Oligo_vs_others/Sign_genes.xlsx", sheetName="UP")
# write.xlsx(underexpr, file="./data_output/PC1_Oligo_vs_others/Sign_genes.xlsx", sheetName="DOWN", append=TRUE)
# write.xlsx(signif, file="./data_output/PC1_Oligo_vs_others/Sign_genes.xlsx", sheetName="SIGNIF", append=TRUE)

```


## Venn diagram of common genes

```{r}




```

But this doesn't take into account the logFc of the change in those genes
Is there a way to score a pathway such as:
- EGF explains 20% of the change in that pathway's enrichment
- Oligo explains the other 80%

```{r, fig.width=5, fig.height=5, eval=FALSE}

# concatenating significant genes 

res_tbl =
  res_tbl %>% 
  na.omit()

res_tbl$comparison = "EGF_Oli_vs_others"
res_egf_tbl$comparison = "EGF_vs_others"
res_oligo_tbl$comparison = "Oligo_vs_others"

fc = 
  list(res_tbl, res_egf_tbl, res_oligo_tbl) %>% 
  purrr::reduce(full_join) %>% 
  dplyr::select(log2FoldChange, gene, comparison) %>% 
  pivot_wider(names_from = comparison,
              values_from = log2FoldChange)

fc_matrix = fc[,2:4] 
rownames(fc_matrix) = fc$gene

fc_matrix = as.matrix(fc_matrix)

# which genes do we want to look at 

fc1 = 
  list(res_tbl, res_egf_tbl, res_oligo_tbl) %>% 
  purrr::reduce(full_join) %>% 
  dplyr::select(log2FoldChange, gene, comparison) %>% 
  filter(log2FoldChange>2) %>% 
  pivot_wider(names_from = comparison,
              values_from = log2FoldChange) 

fc1_matrix = fc1[,2:4]  %>% 
 replace(is.na(.), 0) 
rownames(fc1_matrix) = fc1$gene

fc1_matrix = as.matrix(fc1_matrix)

fc1_matrix = fc1_matrix[fc1_matrix[,1]>0,]

```

```{r, fig.width=5, fig.height=15, eval=FALSE}

aheatmap(fc1_matrix, color = rev(brewer.pal(9,"RdBu")),
         annColors = "Set2")

pheatmap(fc1_matrix, main=" ", cluster_cols=F,
         fontsize_row=3, border_color=NA, scale = "none")

```


## GSEA 

### GOBP
 Get the common terms and facet grid the different comparisons
 
```{r, fig.width=12, fig.height=14}

ordered_genes_fc1 <- res_egf_tbl$log2FoldChange
names(ordered_genes_fc1) <- res_egf_tbl$gene
ordered_genes_fc1 <- sort(ordered_genes_fc1, decreasing = T)

ordered_genes_fc2 <- res_oligo_tbl$log2FoldChange
names(ordered_genes_fc2) <- res_oligo_tbl$gene
ordered_genes_fc2 <- sort(ordered_genes_fc2, decreasing = T)

gcSample = list(Oligomycin = ordered_genes_fc2, 
                EGF = ordered_genes_fc1, 
                both = ordered_genes_fc)

ck = compareCluster(gcSample, fun = GSEA, TERM2GENE = dplyr::select(
    hsa_GOBP_sets,
    gs_name,
    gene_symbol
  ))

dotplot(ck, showCategory = 20, font.size = 7, x = "NES", by = "Count")+
  facet_grid(.~Cluster)+
  scale_colour_gradient2(limits=c(0, 0.05), low="red", high = "blue", 
                         mid = "grey", midpoint = 0.025)+
  labs(title = "GSEA GO:BP",
              subtitle = "Comparing the contributions of EGF and Oligo to the PC1 dimension")

# write.xlsx(ck, "./data_output/PC1_OlEGF_vs_others/GOBPgsea_compare_conditions.xlsx")

```
 

### Reactome
 Get the common terms and facet grid the different comparisons
 
```{r, fig.width=12, fig.height=14}

ck = compareCluster(gcSample, fun = GSEA, TERM2GENE = dplyr::select(
    hsa_reactome_sets,
    gs_name,
    gene_symbol
  ))

dotplot(ck, showCategory = 20, font.size = 7, x = "NES", by = "Count")+
  facet_grid(.~Cluster)+
  scale_colour_gradient2(limits=c(0, 0.05), low="red", high = "blue", 
                         mid = "grey", midpoint = 0.025)+
  labs(title = "GSEA Reactome",
              subtitle = "Comparing the contributions of EGF and Oligo to the PC1 dimension")

# write.xlsx(ck, "./data_output/PC1_OlEGF_vs_others/Reactomegsea_compare_conditions.xlsx")

ggsave(plot = last_plot(), "./figures/Reactome_comp_GSEA.svg", device = "svg", dpi = 300,
       height = 11, width = 8)

```

```{r, fig.width=12, fig.height=14}

ck1n = ck@compareClusterResult$ID[1:10]
ck1 = ck@compareClusterResult %>% 
  filter(ID %in% ck1n)

dotplot(ck1, showCategory = 20, font.size = 7, x = "NES", by = "Count")+
  facet_grid(.~Cluster)+
  scale_colour_gradient2(limits=c(0, 0.05), low="red", high = "blue", 
                         mid = "grey", midpoint = 0.025)+
  labs(title = "GSEA Reactome",
              subtitle = "Comparing the contributions of EGF and Oligo to the PC1 dimension")

# write.xlsx(ck, "./data_output/PC1_OlEGF_vs_others/Reactomegsea_compare_conditions.xlsx")

ggsave(plot = last_plot(), "./figures/Reactome_comp_GSEA.svg", device = "svg", dpi = 300,
       height = 11, width = 8)

```

```{r, fig.height=10, fig.width=12}

targetora = c("REACTOME_UNFOLDED_PROTEIN_RESPONSE_UPR",
               "REACTOME_PERK_REGULATES_GENE_EXPRESSION",
              "REACTOME_IRE1ALPHA_ACTIVATES_CHAPERONES",
              "REACTOME_ATF4_ACTIVATES_GENES_IN_RESPONSE_TO_ENDOPLASMIC_RETICULUM_STRESS",
              "REACTOME_G2_M_CHECKPOINTS" ,
              "REACTOME_MITOTIC_SPINDLE_CHECKPOINT" ,
              "REACTOME_TRNA_AMINOACYLATION",
              "REACTOME_SUMOYLATION_OF_DNA_DAMAGE_RESPONSE_AND_REPAIR_PROTEINS",
               "REACTOME_M_PHASE",

               "REACTOME_CELL_CYCLE_CHECKPOINTS",
               "REACTOME_DNA_DOUBLE_STRAND_BREAK_REPAIR",
               "REACTOME_MITOTIC_METAPHASE_AND_ANAPHASE",
               "REACTOME_HOMOLOGY_DIRECTED_REPAIR",
               "REACTOME_TRANSPORT_TO_THE_GOLGI_AND_SUBSEQUENT_MODIFICATION",
               "REACTOME_ION_TRANSPORT_BY_P_TYPE_ATPASES",
               "REACTOME_CYTOCHROME_P450_ARRANGED_BY_SUBSTRATE_TYPE",
               "REACTOME_ATF6_ATF6_ALPHA_ACTIVATES_CHAPERONES",
               "REACTOME_ER_TO_GOLGI_ANTEROGRADE_TRANSPORT",
               "REACTOME_INTRA_GOLGI_AND_RETROGRADE_GOLGI_TO_ER_TRAFFIC",
               "REACTOME_SIGNALING_BY_PDGF",
               "REACTOME_TRANSLATION",
               "REACTOME_FATTY_ACID_METABOLISM",
               "REACTOME_THE_CITRIC_ACID_TCA_CYCLE_AND_RESPIRATORY_ELECTRON_TRANSPORT",
               "REACTOME_GENE_SILENCING_BY_RNA", 
               "REACTOME_DNA_DAMAGE_TELOMERE_STRESS_INDUCED_SENESCENCE",
              
               "REACTOME_TRNA_PROCESSING_IN_THE_NUCLEUS",
               "REACTOME_CYTOSOLIC_TRNA_AMINOACYLATION",
               "REACTOME_ACTIVATION_OF_ATR_IN_RESPONSE_TO_REPLICATION_STRESS",
               "REACTOME_REGULATION_OF_TP53_ACTIVITY_THROUGH_PHOSPHORYLATION",
               "REACTOME_SIGNALING_BY_EGFR",
               "REACTOME_RECOGNITION_OF_DNA_DAMAGE_BY_PCNA_CONTAINING_REPLICATION_COMPLEX",
               "REACTOME_OXIDATIVE_STRESS_INDUCED_SENESCENCE")

partial = 
ck %>% 
  filter(ck@compareClusterResult$ID %in% targetora)

dotplot(partial, showCategory = 50, font.size = 8, x = "NES", by = "Count")+
  facet_grid(.~Cluster)+
  scale_colour_gradient2(limits=c(0, 0.05), low="red", high = "blue", 
                         mid = "grey", midpoint = 0.025)+
  labs(title = "GSEA Reactome",
              subtitle = "Comparing the contributions of EGF and Oligo to the PC1 dimension")

ggsave(plot = last_plot(), "./figures/Reactome_comp1_GSEA.svg", device = "svg", dpi = 300,
       height = 12, width = 12)

```


```{r}
sessionInfo()
```
