---
title: "MCF10A metabolism screen"
author: "Marion Hardy"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true 
    theme: spacelab 
    highlight: monochrome
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, cache = TRUE, echo = FALSE, warning = F, cache.lazy = F)
knitr::opts_chunk$set(fig.width=10, fig.height=15) 

library(RColorBrewer)
library(tidyverse)
library(DESeq2)
library(tidyverse)
library(cowplot)
library(biomaRt)
library(ggrepel)
library(RColorBrewer)
library(pheatmap)
library(xlsx)
library(msigdbr)
library(clusterProfiler)

```

```{r Data loading, include=FALSE}

counts <- as.data.frame(read.csv("./data/MCF10A_counts.csv", row.names = 1))
coldata = read.csv("./data/coldata.csv")
counts = counts[,-1]

```

# Introduction

Analysis of MCF10A in 16 different conditions 2 biological replicates
per sample

# Quality check
## Size factors and Dispersion plot

```{r, fig.height=4, fig.width=6}

dds <- DESeqDataSetFromMatrix(countData = counts, colData = coldata,
                              design = ~condition+replicate) 

# Generate a linear model

dds$condition <- relevel(dds$condition, "IM")
dds <- DESeq(dds)
saveRDS(dds, file = "./data_output/All_vs_IM_dds.rds")

# Checking size factors and dispersion

sizeFactors(dds) %>% 
  knitr::kable()

plotDispEsts(dds) # verifies normalization, graph looks a-ok

```

# PCA

## All conditions

```{r, fig.height=6, fig.width=12}
# Checking PCA

rld <- vst(dds)

p1 <- plotPCA(rld,intgroup="condition") + 
  geom_text_repel(max.overlaps = 15,
                  box.padding = 0.25,
                  segment.color = 'grey50',
                  fontface = "italic",
                  label = rld$condition)+
  labs(title = 'PCA per condition')

p2 <- plotPCA(rld,intgroup="replicate") + 
  geom_text_repel(max.overlaps = 15,
                  box.padding = 0.25,
                  segment.color = 'grey50',
                  fontface = "italic",
                  label = rld$replicate)+
  labs(title = 'PCA per condition')

plot_grid(p1, p2, ncol = 2, align = "hv")

```

## Better separation on that central cluster

Removal of - Oligomycin - EGF positive - Growth medium - IL6 - IM HC
neg - IM ins neg

```{r, fig.height=6, fig.width=12}
# Checking PCA

dds1 = dds[,dds$condition %in% c('IM','IM_Glutamine_pos',
                        'IM_Glucose_neg','IM_CT_neg','AMPK_activator',
                        'AKT_inhibitor','ERK_inhibitor','mTORC1_inhibitor',
                        'MPC_inhibitor','LDH_inhibitor')]
rld1 <- vst(dds1)

p3 <- plotPCA(rld1,intgroup="condition") + 
  geom_text_repel(max.overlaps = 15,
                  box.padding = 0.25,
                  segment.color = 'grey50',
                  fontface = "italic",
                  label = rld1$condition)+
  labs(title = 'PCA per condition: Specific conditions selected')

p4 <- plotPCA(rld1,intgroup="replicate") + 
  geom_text_repel(max.overlaps = 15,
                  box.padding = 0.25,
                  segment.color = 'grey50',
                  fontface = "italic",
                  label = rld1$replicate)+
  labs(title = 'PCA per condition: Specific conditions selected')

plot_grid(p3, p4, ncol = 2, align = "hv")
```

I think we can see a pretty evident batch effect per replicate!

## Attempt to correct the batch effect

```{r, fig.height=8, fig.width=12}
# Checking PCA

vsd = vst(dds)
vsd1 = vsd
assay(vsd1) <- limma::removeBatchEffect(assay(vsd), vsd$replicate)

p5 <- plotPCA(vsd,intgroup="replicate") + 
  geom_text_repel(max.overlaps = 15,
                  box.padding = 0.25,
                  segment.color = 'grey50',
                  fontface = "italic",
                  label = vsd$condition)+
  labs(title = 'Completed data: PCA not corrected')

p6 <- plotPCA(vsd1,intgroup="replicate") + 
  geom_text_repel(max.overlaps = 15,
                  box.padding = 0.25,
                  segment.color = 'grey50',
                  fontface = "italic",
                  label = vsd1$condition)+
  labs(title = 'Completed data: PCA corrected')

# Just on the clustered data

dds1 = dds[,dds$condition %in% c('IM','IM_Glutamine_pos',
                        'IM_Glucose_neg','IM_CT_neg','AMPK_activator',
                        'AKT_inhibitor','ERK_inhibitor','mTORC1_inhibitor',
                        'MPC_inhibitor','LDH_inhibitor')]

vsd = vst(dds1)
vsd1 = vsd
assay(vsd1) <- limma::removeBatchEffect(assay(vsd), vsd$replicate)

p7 <- plotPCA(vsd,intgroup="replicate") + 
  geom_text_repel(max.overlaps = 15,
                  box.padding = 0.25,
                  segment.color = 'grey50',
                  fontface = "italic",
                  label = vsd$condition)+
  labs(title = 'Filtered data: PCA not corrected')

p8 <- plotPCA(vsd1,intgroup="replicate") + 
  geom_text_repel(max.overlaps = 15,
                  box.padding = 0.25,
                  segment.color = 'grey50',
                  fontface = "italic",
                  label = vsd1$condition)+
  labs(title = 'Filtered data: PCA corrected')

plot_grid(p5, p6, p7, p8, ncol = 2, nrow = 2, align = "hv")

```

I think we can see a pretty evident batch effect per replicate!

# Distance matrix

## Look at the batch effect disappear

```{r, fig.height=8, fig.width=8}

vsd = vst(dds)

# Checking sample similarity

sampleDists <- dist(t(assay(vsd)))
sampleDistMatrix <- as.matrix(sampleDists)
rownames(sampleDistMatrix) <- paste(vsd$condition, sep="-")
colnames(sampleDistMatrix) <- paste(vsd$condition, sep="-")
colors <- colorRampPalette(rev(brewer.pal(9, "Blues")) )(255)
pheatmap(sampleDistMatrix,
         clustering_distance_rows=sampleDists,
         clustering_distance_cols=sampleDists,
         col=colors)

```

```{r, fig.height=8, fig.width=8}

assay(vsd) <- limma::removeBatchEffect(assay(vsd), vsd$replicate)

# Checking sample similarity

sampleDists <- dist(t(assay(vsd)))
sampleDistMatrix <- as.matrix(sampleDists)
rownames(sampleDistMatrix) <- paste(vsd$condition, sep="-")
colnames(sampleDistMatrix) <- paste(vsd$condition, sep="-")
colors <- colorRampPalette(rev(brewer.pal(9, "Blues")) )(255)
pheatmap(sampleDistMatrix,
         clustering_distance_rows=sampleDists,
         clustering_distance_cols=sampleDists,
         col=colors)

```

Same thing here, the batch effect can seen and disappears with the limma::removeBatchEffect function. Meaning I need to include replicates in the design formula.

# Comparaisons of interest
## What should we pick?

```{r}
resultsNames(dds) %>% 
  knitr::kable()
```

Maybe
- Oligomycin vs IM
- EGF vs IM
- EGF vs Oligomycin

## Oligomycin vs IM

```{r}

## OlIM  -----------------------------------------------------------------------

res <- results(dds, name = "condition_Oligomycin_vs_IM")
res_tbl <- as_tibble(res, rownames="ensembl")

# Import annotation file

ensembl_to_geneName <- readRDS("./data/hsapiens_annotations_230510.rds") %>% 
  filter(!duplicated(gene, drop = F))

# Add gene names and entrez id to your results

res_tbl <- res_tbl %>%
  left_join(ensembl_to_geneName) %>%
  arrange(padj) 

write.csv(res_tbl,"./data_output/Oligomycin_vs_IM/res_tbl.csv", row.names = T)

# plotMA(res) # looks good

# Save the signif genes

overexpr <- res_tbl %>% filter(padj<=0.05 & log2FoldChange>=1) 
underexpr <- res_tbl %>% filter(padj<=0.05 & log2FoldChange<=-1)
signif <- full_join(overexpr, underexpr)

write.xlsx(overexpr, file="./data_output/Oligomycin_vs_IM/Sign_genes.xlsx", sheetName="UP")
write.xlsx(underexpr, file="./data_output/Oligomycin_vs_IM/Sign_genes.xlsx", sheetName="DOWN", append=TRUE)
write.xlsx(signif, file="./data_output/Oligomycin_vs_IM/Sign_genes.xlsx", sheetName="SIGNIF", append=TRUE)

```

### Volcano plots

```{r, fig.height=6, fig.width=8}
# Volcano plot

p1 =
res_tbl %>%
  filter(!is.na(padj)) %>%
  ggplot(aes(x = log2FoldChange, y = -log10(padj),
             color = padj < 0.05 & abs(log2FoldChange) > 1, 
             label = ifelse(padj<0.05&log2FoldChange>=1|
                              padj<0.05&log2FoldChange<=-1,as.character(gene),''))) +
  scale_colour_manual(values = c("gray", "firebrick3")) +
  labs(col="Significantly expressed")+
  geom_point(size = 0.5) +
  geom_hline(yintercept = -log10(0.05)) +
  geom_vline(xintercept = 1) +
  geom_vline(xintercept = -1)+
  geom_text_repel(max.overlaps = 15,
                  box.padding = 0.25,
                  segment.color = 'grey50',
                  fontface = "italic")+
  labs(title = "Oligomycin_vs_IM")+
  theme_bw()

print(p1)

ggsave("./figures/Oligomycin_vs_IM/volcanoplot.png", last_plot(), dpi= 500, width = 12, height = 8)

```

### GSEA analysis (logFc)

```{r}

ordered_genes_fc <- res_tbl$log2FoldChange
names(ordered_genes_fc) <- res_tbl$gene
ordered_genes_fc <- sort(ordered_genes_fc, decreasing = T)

```

```{r}

# MsigDb

hsa_GOBP_sets <- msigdbr(
  species = "Homo sapiens", 
  category = "C5",
  subcategory = "GO:BP")

hsa_GOMF_sets <- msigdbr(
  species = "Homo sapiens", 
  category = "C5",
  subcategory = "GO:MF")

hsa_GOCC_sets <- msigdbr(
  species = "Homo sapiens", 
  category = "C5",
  subcategory = "GO:CC") 

hsa_reactome_sets <- msigdbr(
  species = "Homo sapiens", 
  category = "C2",
  subcategory = "CP:REACTOME") # for reactome collection

hsa_kegg_sets <- msigdbr(
  species = "Homo sapiens", 
  category = "C2",
  subcategory = "CP:KEGG") # for KEGG collection

hsa_wiki_sets <- msigdbr(
  species = "Homo sapiens", 
  category = "C2",
  subcategory = "CP:WIKIPATHWAYS") # for Wikipathways collection

set.seed(054057) # for reproducibility

```

#### GOBP

```{r, fig.height=8, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.1, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_GOBP_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GSEA GO:BP Oligomycin vs imaging media")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/Oligomycin_vs_IM/GOBPgsea.svg", dpi = 300,
       height = 8, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/Oligomycin_vs_IM/GOBPgsea.xlsx")

```

```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)
```

#### GOMF

```{r, fig.height=8, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_GOMF_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GSEA GO:MF Oligomycin vs imaging media")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/Oligomycin_vs_IM/GOMFgsea.svg", dpi = 300,
       height = 8, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/Oligomycin_vs_IM/GOMFgsea.xlsx")

```

```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)
```

#### Reactome

```{r, fig.height=8, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_reactome_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GSEA Reactome Oligomycin vs imaging media")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/Oligomycin_vs_IM/Reactomegsea.svg", dpi = 300, height = 8, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/Oligomycin_vs_IM/Reactomegsea.xlsx")

```

```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)
```


#### KEGG

```{r, fig.height=8, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_kegg_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GSEA KEGG Oligomycin vs imaging media")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/Oligomycin_vs_IM/KEGGgsea.svg", dpi = 300,
       height = 8, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/Oligomycin_vs_IM/KEGGgsea.xlsx")

```


```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)
```

#### Wikipathways

```{r, fig.height=8, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_wiki_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GSEA Wikipathways Oligomycin vs imaging media")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/Oligomycin_vs_IM/wikigsea.svg", dpi = 300,
       height = 8, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/Oligomycin_vs_IM/wikigsea.xlsx")

```


```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)
```

## EGF vs IM
```{r}
## EGFIM-----------------------------------------------------------------------

res <- results(dds, name = "condition_IM_EGF_pos_vs_IM")
res_tbl <- as_tibble(res, rownames="ensembl")

# Import annotation file

ensembl_to_geneName <- readRDS("./data/hsapiens_annotations_230510.rds") %>% 
  filter(!duplicated(gene, drop = F))

# Add gene names and entrez id to your results

res_tbl <- res_tbl %>%
  left_join(ensembl_to_geneName) %>%
  arrange(padj) 

write.csv(res_tbl,"./data_output/EGF_pos_vs_IM/res_tbl.csv", row.names = T)

# plotMA(res) # looks good

# Save the signif genes

overexpr <- res_tbl %>% filter(padj<=0.05 & log2FoldChange>=1) 
underexpr <- res_tbl %>% filter(padj<=0.05 & log2FoldChange<=-1)
signif <- full_join(overexpr, underexpr)

write.xlsx(overexpr, file="./data_output/EGF_pos_vs_IM/Sign_genes.xlsx", sheetName="UP")
write.xlsx(underexpr, file="./data_output/EGF_pos_vs_IM/Sign_genes.xlsx", sheetName="DOWN", append=TRUE)
write.xlsx(signif, file="./data_output/EGF_pos_vs_IM/Sign_genes.xlsx", sheetName="SIGNIF", append=TRUE)

```

### Volcano plot

```{r, fig.height=6, fig.width=8}

# Volcano plot

p2 =
res_tbl %>%
  filter(!is.na(padj)) %>%
  ggplot(aes(x = log2FoldChange, y = -log10(padj),
             color = padj < 0.05 & abs(log2FoldChange) > 1, 
             label = ifelse(padj<0.05&log2FoldChange>=1|
                              padj<0.05&log2FoldChange<=-1,as.character(gene),''))) +
  scale_colour_manual(values = c("gray", "firebrick3")) +
  labs(col="Significantly expressed")+
  geom_point(size = 0.5) +
  geom_hline(yintercept = -log10(0.05)) +
  geom_vline(xintercept = 1) +
  geom_vline(xintercept = -1)+
  geom_text_repel(max.overlaps = 15,
                  box.padding = 0.25,
                  segment.color = 'grey50',
                  fontface = "italic")+
  labs(title = "EGF_pos_vs_IM")+
  theme_bw()

print(p2)

ggsave("./figures/EGF_pos_vs_IM/volcanoplot.png", last_plot(), dpi= 500, width = 12, height = 8)

```

### GSEA analysis (logFc)

```{r}

ordered_genes_fc <- res_tbl$log2FoldChange
names(ordered_genes_fc) <- res_tbl$gene
ordered_genes_fc <- sort(ordered_genes_fc, decreasing = T)

```

#### GOBP

```{r, fig.height=8, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.1, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_GOBP_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GSEA GO:BP Imaging media EGF+ vs -")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/EGF_pos_vs_IM/GOBPgsea.svg", dpi = 300,
       height = 8, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/EGF_pos_vs_IM/GOBPgsea.xlsx")

```

```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)
```

#### GOMF

```{r, fig.height=8, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_GOMF_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GSEA GO:MF Imaging media EGF+ vs -")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/EGF_pos_vs_IM/GOMFgsea.svg", dpi = 300,
       height = 8, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/EGF_pos_vs_IM/GOMFgsea.xlsx")

```

```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)
```

#### Reactome

```{r, fig.height=8, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_reactome_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GSEA Reactome Imaging media EGF+ vs -")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/EGF_pos_vs_IM/Reactomegsea.svg", dpi = 300, height = 8, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/EGF_pos_vs_IM/Reactomegsea.xlsx")

```

```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)
```

#### KEGG

```{r, fig.height=8, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_kegg_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GSEA KEGG Imaging media EGF+ vs -")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/EGF_pos_vs_IM/KEGGgsea.svg", dpi = 300,
       height = 8, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/EGF_pos_vs_IM/KEGGgsea.xlsx")

```


```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)
```

#### Wikipathways

```{r, fig.height=8, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_wiki_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GSEA Wikipathways Imaging media EGF+ vs -")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/EGF_pos_vs_IM/wikigsea.svg", dpi = 300,
       height = 8, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/EGF_pos_vs_IM/wikigsea.xlsx")

```


```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)
```

## Oligomycin vs EGF

```{r}
## OMEGF-----------------------------------------------------------------------
# Generate a linear model

dds$condition <- relevel(dds$condition, "IM_EGF_pos")
dds <- DESeq(dds)
saveRDS(dds, file = "./data_output/All_vs_IM_EGF_dds.rds")

resultsNames(dds) %>% 
  knitr::kable()

res <- results(dds, name = "condition_Oligomycin_vs_IM_EGF_pos")
res_tbl <- as_tibble(res, rownames="ensembl")

# Import annotation file

ensembl_to_geneName <- readRDS("./data/hsapiens_annotations_230510.rds") %>% 
  filter(!duplicated(gene, drop = F))

# Add gene names and entrez id to your results

res_tbl <- res_tbl %>%
  left_join(ensembl_to_geneName) %>%
  arrange(padj) 

write.csv(res_tbl,"./data_output/Oligomycin_vs_IM_EGF_pos/res_tbl.csv", row.names = T)

# plotMA(res) # looks good

# Save the signif genes

overexpr <- res_tbl %>% filter(padj<=0.05 & log2FoldChange>=1) 
underexpr <- res_tbl %>% filter(padj<=0.05 & log2FoldChange<=-1)
signif <- full_join(overexpr, underexpr)

write.xlsx(overexpr, file="./data_output/Oligomycin_vs_IM_EGF_pos/Sign_genes.xlsx", sheetName="UP")
write.xlsx(underexpr, file="./data_output/Oligomycin_vs_IM_EGF_pos/Sign_genes.xlsx", sheetName="DOWN", append=TRUE)
write.xlsx(signif, file="./data_output/Oligomycin_vs_IM_EGF_pos/Sign_genes.xlsx", sheetName="SIGNIF", append=TRUE)

```

### Volcano plot

```{r, fig.height=6, fig.width=8}

# Volcano plot

p3 =
res_tbl %>%
  filter(!is.na(padj)) %>%
  ggplot(aes(x = log2FoldChange, y = -log10(padj),
             color = padj < 0.05 & abs(log2FoldChange) > 1, 
             label = ifelse(padj<0.05&log2FoldChange>=1|
                              padj<0.05&log2FoldChange<=-1,as.character(gene),''))) +
  scale_colour_manual(values = c("gray", "firebrick3")) +
  labs(col="Significantly expressed")+
  geom_point(size = 0.5) +
  geom_hline(yintercept = -log10(0.05)) +
  geom_vline(xintercept = 1) +
  geom_vline(xintercept = -1)+
  geom_text_repel(max.overlaps = 15,
                  box.padding = 0.25,
                  segment.color = 'grey50',
                  fontface = "italic")+
  labs(title = "Oligomycin_vs_IM_EGF_pos")+
  theme_bw()

print(p3)

ggsave("./figures/Oligomycin_vs_IM_EGF_pos/volcanoplot.png", last_plot(), dpi= 500, width = 12, height = 8)

```

### GSEA analysis (logFc)

```{r}

ordered_genes_fc <- res_tbl$log2FoldChange
names(ordered_genes_fc) <- res_tbl$gene
ordered_genes_fc <- sort(ordered_genes_fc, decreasing = T)

```

##### GOBP

```{r, fig.height=8, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.1, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_GOBP_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GSEA GO:BP IM : Oligomycin vs EGF")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/Oligomycin_vs_IM_EGF_pos/GOBPgsea.svg", dpi = 300,
       height = 8, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/Oligomycin_vs_IM_EGF_pos/GOBPgsea.xlsx")

```

```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)
```

##### GOMF

```{r, fig.height=3, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_GOMF_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GSEA GO:MF IM : Oligomycin vs EGF")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/Oligomycin_vs_IM_EGF_pos/GOMFgsea.svg", dpi = 300,
       height = 8, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/Oligomycin_vs_IM_EGF_pos/GOMFgsea.xlsx")

```

```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)
```

##### Reactome

```{r, fig.height=8, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_reactome_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GSEA Reactome IM : Oligomycin vs EGF")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/Oligomycin_vs_IM_EGF_pos/Reactomegsea.svg", dpi = 300, height = 8, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/Oligomycin_vs_IM_EGF_pos/Reactomegsea.xlsx")

```

```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)
```

##### KEGG

```{r, fig.height=4, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_kegg_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GSEA KEGG IM : Oligomycin vs EGF")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/Oligomycin_vs_IM_EGF_pos/KEGGgsea.svg", dpi = 300,
       height = 8, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/Oligomycin_vs_IM_EGF_pos/KEGGgsea.xlsx")

```


```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)
```


##### Wikipathways

```{r, fig.height=3, fig.width=7}

gsea_results <- GSEA(
  geneList = ordered_genes_fc, 
  pvalueCutoff = 0.05, 
  eps = 0, 
  pAdjustMethod = "BH", 
  nPermSimple = 10000,
  TERM2GENE = dplyr::select(
    hsa_wiki_sets,
    gs_name,
    gene_symbol
  )
)

dotplot(gsea_results, x = "NES", showCategory = 30, font.size = 7)+ 
  labs(title = "GSEA",
              subtitle = "GSEA Wikipathways IM : Oligomycin vs EGF")+
   theme(axis.line = element_line(color='black'),
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

ggsave(plot = last_plot(), "./figures/Oligomycin_vs_IM_EGF_pos/wikigsea.svg", dpi = 300,
       height = 8, width = 8, device = "svg")

write.xlsx(gsea_results, "./data_output/Oligomycin_vs_IM_EGF_pos/wikigsea.xlsx")

```


```{r}

cnetplot(gsea_results, foldChange=ordered_genes_fc, showCategory = 50,
         cex_label_category = .5, cex_label_gene = .5)
```


```{r, fig.height=12, fig.width=16}
plot_grid(p1, p2, p3, ncol = 2, nrow = 2, align = "hv")
```



```{r}
sessionInfo()
```
